### 2024-01-11 docs/projects/noj/ml.qmd
rerendered noj ml doc

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7698     -0.2528      0.0188      0.2103      0.5987

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.8690     0.2997     6.2352     0.0000 ***
sepal-width         0.6645     0.0791     8.3956     0.0000 ***
petal-length        0.7226     0.0722    10.0028     0.0000 ***
petal-width        -0.6541     0.1594    -4.1043     0.0001 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3154 on 96 degrees of freedom
Multiple R-squared: 0.8466,    Adjusted R-squared: 0.8418
F-statistic: 176.6175 on 4 and 96 DF,  p-value: 6.018e-39

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7900     -0.2237      0.0394      0.2235      0.8037

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.7690     0.3120     5.6689     0.0000 ***
sepal-width         0.6801     0.0844     8.0599     0.0000 ***
petal-length        0.7043     0.0664    10.6014     0.0000 ***
petal-width        -0.5256     0.1508    -3.4858     0.0007 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3057 on 96 degrees of freedom
Multiple R-squared: 0.8690,    Adjusted R-squared: 0.8649
F-statistic: 212.1968 on 4 and 96 DF,  p-value: 3.179e-42
